---
title: "Models and Predictions for Hit/Miss POD Data"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  word_document: default
---

Choose one of the four distributions.
```{r}
Distribution="Log_Log"
#Distribution="Weib_Log"
#Distribution="Weib_Weib"
#Distribution="Unif_Unif"

```

Input the combination(s) of overlap, evenness and sample size (n) at which to predict the percent bias. 
```{r}
# Input a vector c(0,1,2) or a value.
  # Overlap should be between 0 and 0.7
  # Evenness should be between 0 and 0.5
  # n is sample size

n        = c(60, 60)  
overlap  = c(0.36667, 0.36667)
evenness = c(0.16667, 0.5)
CI = "all" # "LR", "MLR", "Std. Wald", "Mod. Wald"

```

Set folder to the location where the github files are saved. 
```{r}
folder = "C:/Users/chriz/GitRepositories/HitMissPaperData/"
```

Predicted Percent Bias in a9095 Estimation (uses Likelihood Ratio for Calculating a9095):
```{r, warning=FALSE, echo=FALSE}
source(paste(folder,"predict_a9095_percent_bias.R",sep=""))
source(paste(folder,"getPredictedBiasPerCI.R",sep=""))


if(CI=="all"){
  load(paste(folder,Distribution,"_a9095_Percent_Bias_Models_ModWald.RData", sep=""))
  load(paste(folder,Distribution,"_a9095_Percent_Bias_Models_StdWald.RData", sep=""))
  load(paste(folder,Distribution,"_a9095_Percent_Bias_Models_LR.RData", sep=""))
  load(paste(folder,Distribution,"_a9095_Percent_Bias_Models_MLR.RData", sep=""))
  }else{
  LoadLocation = switch(
    CI,
    "Mod. Wald"  = paste(folder,Distribution,"_a9095_Percent_Bias_Models_ModWald.RData", sep=""),
    "Std. Wald"  = paste(folder,Distribution,"_a9095_Percent_Bias_Models_StdWald.RData", sep=""),
    "LR"         = paste(folder,Distribution,"_a9095_Percent_Bias_Models_LR.RData", sep=""),
    "MLR"        = paste(folder,Distribution,"_a9095_Percent_Bias_Models_MLR.RData", sep="")
  )
  load(LoadLocation)
}

if(CI=="Mod. Wald"|CI=="all"){
  print(paste("The Model for Percent Bias in a9095 for",Distribution, 
              "using a Standard Wald Confidence Interval for a9095 is as follows:"))
  summary(a9095.Wald.old.boxcox.perc)
}
if(CI=="Std. Wald"|CI=="all"){
  print(paste("The Model for Percent Bias in a9095 for",Distribution, 
            "using a Modified Wald Confidence Interval for a9095 is as follows:"))
  summary(a9095.Wald.boxcox.perc)
}
if(CI=="LR"|CI=="all"){
  print(paste("The Model for Percent Bias in a9095 for",Distribution, 
            "using a Likelihood Ratio Confidence Interval for a9095 is as follows:"))
  summary(a9095.LR.boxcox.perc)
}  
if(CI=="MLR"|CI=="all"){
  print(paste("The Model for Percent Bias in a9095 for",Distribution, 
            "using a Modified Likelihood Ratio Confidence Interval for a9095 is as follows:"))
  summary(a9095.MLR.boxcox.perc)
}

(predicted_a9095_percent_bias = predict_a9095_percent_bias(folder, Distribution, overlap, evenness, n, CI))

```

Predict Probability of a9095 not existing (uses Likelihood Ratio for Calculating a9095):
```{r, warning=FALSE, echo=FALSE}
source(paste(folder,"predict_a9095_risk.R",sep=""))
source(paste(folder,"getPredictedExistencePerCI.R",sep=""))

if(CI=="all"){
  load(paste(folder,Distribution,"_a9095_Probability_of_Not_Existing_ModWald.RData", sep=""))
  load(paste(folder,Distribution,"_a9095_Probability_of_Not_Existing_StdWald.RData", sep=""))
  load(paste(folder,Distribution,"_a9095_Probability_of_Not_Existing_LR.RData", sep=""))
  load(paste(folder,Distribution,"_a9095_Probability_of_Not_Existing_MLR.RData", sep=""))
  }else{
  LoadLocation = switch(
    CI,
    "Mod. Wald"  = paste(folder,Distribution,"_a9095_Probability_of_Not_Existing_ModWald.RData", sep=""),
    "Std. Wald"  = paste(folder,Distribution,"_a9095_Probability_of_Not_Existing_StdWald.RData", sep=""),
    "LR"         = paste(folder,Distribution,"_a9095_Probability_of_Not_Existing_LR.RData", sep=""),
    "MLR"        = paste(folder,Distribution,"_a9095_Probability_of_Not_Existing_MLR.RData", sep="")
  )
  load(LoadLocation)
}



if(CI=="Mod. Wald"|CI=="all"){
  print(paste("The Model for probability of a9095 not existing when using a standard Wald  confidence interval for a9095 and for",Distribution, "is as follows:"))
  summary(Wald.old.a9095.exist)
}
if(CI=="Std. Wald"|CI=="all"){
  print(paste("The Model for probability of a9095 not existing when using a modified Wald     confidence interval for a9095 and for",Distribution, "is as follows:"))
  summary(Wald.a9095.exist)
}
if(CI=="LR"|CI=="all"){
  print(paste("The Model for probability of a9095 not existing when using a Likelihood Ratio   confidence interval for a9095 and for",Distribution, "is as follows:"))
  summary(LR.a9095.exist)
}  
if(CI=="MLR"|CI=="all"){
  print(paste("The Model for probability of a9095 not existing when using a Modified Likelihood Ratio confidence interval for a9095 and for",Distribution, "is as follows:"))
  summary(MLR.a9095.exist)
}

(predicted_a9095_risk_not_exist = predict_a9095_risk(folder, Distribution, overlap, evenness, n, CI))

```


Predicted Percent Bias in a90 Estimation:
```{r, warning=FALSE, echo=FALSE}
source(paste(folder,"predict_a90_percent_bias.R",sep=""))

load(paste(folder,Distribution,"_a90_Percent_Bias_Models.RData", sep=""))

print(paste("The Model for Percent Bias in a90 for",Distribution, "is as follows:"))
summary(a90.Wald.boxcox.perc)

(predicted_a90_percent_bias = predict_a90_percent_bias(folder, Distribution, overlap, evenness, n))

```
